---
output: 
  beamer_presentation:
    slide_level: 2
    template: theme/template.tex
    latex_engine: lualatex
    keep_tex: true

# set theme
eco-bielefeld: true
unibi-font: true
emoji: true
fontsize: 10pt
handout: false
aspectratio: 169

# set title, presenter, institute, date
title: "Reusable Beamer + R Markdown Template"
subtitle: "Demonstration deck"
author:
- \underline{Presenter Name}
- Contributor Name
institute: "Institute / Team"
date: "`r format(Sys.Date(), '%d.%m.%Y')`"

# define table of contents
toc: true
toc-depth: 1
toc-title: "Outline"

# define last slide
last-slide: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  out.height = "65%",
  fig.path = "figures/"
)
```

<!--
This file is both a demo and a starting point.
Edit content sections, keep the YAML header, and render with:
rmarkdown::render("slides.Rmd")
-->

# Introduction

## Welcome

This template is designed for professional Beamer slides built from R Markdown.

- Consistent visual style (Bielefeld theme)
- Native support for R plots, tables, and code chunks
- Useful helper commands for appendix navigation

\small Tip: Use section headers (`#`) to create TOC entries and divider slides.

## Agenda

- Context and goals
- Content building blocks
- Appendix navigation buttons
- Backup slides

# Content examples

## Standard text slide

A good slide keeps one main message and a few supporting points.

- Put the headline in the title
- Use short phrases (not paragraphs)
- Explain details verbally while presenting

## Bullet lists and nested bullets

- Project status
  - Data collection complete
  - First model version validated
  - Draft report in preparation
- Next milestone: stakeholder review

## Two-column layout

\begin{columns}[T,totalwidth=\textwidth]
\column{0.52\textwidth}
### Key points

- Left column for narrative
- Good for side-by-side comparisons
- Keeps dense content readable

\column{0.46\textwidth}
### Snapshot

\begin{block}{KPI summary}
\begin{itemize}
  \item Conversion: 7.9\%
  \item Retention: 84\%
  \item Revenue growth: +12\%
\end{itemize}
\end{block}
\end{columns}

## Image example

Use figures from chunks or include external files directly.

```{r, cars_plot, echo = FALSE, fig.cap = "Base R example plot from `cars`."}
plot(cars, pch = 19, col = "steelblue")
abline(lm(dist ~ speed, data = cars), col = "firebrick", lwd = 2)
```

## Table example

```{r, echo=FALSE}
knitr::kable(
  data.frame(
    Scenario = c("Baseline", "Pilot", "Target"),
    Cost = c(100, 115, 120),
    Impact = c("-", "+6%", "+10%")
  ),
  align = c("l", "r", "r"),
  caption = "Illustrative planning table"
)
```

## Code block example

```r
library(dplyr)

summary_tbl <- sales_df %>%
  group_by(region) %>%
  summarise(avg_revenue = mean(revenue, na.rm = TRUE))
```

## Mathematical notation

For model documentation or methods slides:

$$
\hat{\beta} = (X^\top X)^{-1}X^\top y, \qquad
\E[Y \mid X] = X\beta
$$

\small You can use inline math too, e.g. $\alpha \in \R$.

## Quote / highlight

\begin{quote}
"Good slides support a story; they should not compete with it."
\end{quote}

\begin{exampleblock}{Practical suggestion}
Move technical derivations to the appendix and link them with a button.
\end{exampleblock}

## Blocks: alert, example, standard

\begin{block}{Block}
Use for neutral structure.
\end{block}

\begin{exampleblock}{Example block}
Use for positive or recommended actions.
\end{exampleblock}

\begin{alertblock}{Alert block}
Use for risks, caveats, or assumptions.
\end{alertblock}

## Footnote and small reference text

Main takeaway: assumptions must be explicit.\footnote{Illustrative footnote text for template users.}

\vspace{0.5em}
{\scriptsize Reference: Doe, J. (2025). *Practical Presentation Design*.}

# Appendix navigation demo

## Main slide with appendix button
\hypertarget{main_results_slide}{}

This slide links to a detailed backup slide.

- Keep main message here
- Move technical detail to appendix

\appendixbutton{backup_model_details}{Details in appendix}

## Another content slide

Continue with your regular narrative after adding a button-based detour.

# Appendix

## Backup: model details
\hypertarget{backup_model_details}{}

Additional diagnostics and assumptions can live here.

- Residual checks passed
- Sensitivity tested for two alternative specifications
- Full output available on request

\returnbutton{main_results_slide}{Back to main slide}
