---
output: 
  beamer_presentation:
    slide_level: 2               # level-1 heading are sections, level-2 frames
    template: theme/template.tex # location of template file
    latex_engine: lualatex       # or pdflatex, xelatex
    keep_tex: true               # keep .tex file for debugging

# set theme
unibi-font: true
fontsize: 10pt
handout: false
aspectratio: 169

# set title, presenter, institute, date
title: "Title of Presentation"
short-title: "Short Title"
subtitle: "Subtitle"
author:
- \underline{Presenter Name}
- Contributor Name
institute: "Bielefeld University, Department Empirical Methods"
date: "`r format(Sys.Date(), '%d %B %Y')`"

# define table of contents
toc: true
toc-depth: 1
toc-title: "Outline"

# define last slide
last-slide: true
last-slide-message: "Thanks for your attention!"
last-slide-email: name@example.com
last-slide-website: https://example.com
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  out.height = "65%",
  fig.path = "figures/"
)

library("tidyverse")
```

# Introduction

## Welcome

This template is designed for Beamer slides built from R Markdown. 

\vskip 1em

It follows a Bielefeld University / Empirical Methods theme.

\vskip 1em

Feel free to use it at your own risk.

# Content Examples

## Buttons, Columns, Lists, Tables

\hypertarget{buttons_slide}{}

\begin{columns}[T,totalwidth=\textwidth]
\column{0.3\textwidth}
Left

\hfill

\column{0.3\textwidth}
Middle

\hfill

\column{0.3\textwidth}
Right

\end{columns}

\vfill

This slide links to a detailed backup slide. 

\appendixbutton{backup_column_details}{Details}

- Idea:
  - keep main message here
  - move technical detail to appendix
- You can also click the topleft logo to jump to appendix

\vfill

| Scenario | Cost | Impact |
|:---------|-----:|-------:|
| Baseline | 100  |        |
| Pilot    | 115  |  +6 \% |
| Target   | 120  | +10 \% |

## \lang{R}\ Code and Output

```{r}
starwars |>
  select(name, species, homeworld) |>
  print(n = 3)
```

## Images from \lang{R}\ Code

```{r, starwars, echo = FALSE, fig.cap = "Species in Star Wars"}
starwars |>
  count(species, sort = TRUE) |>
  filter(!is.na(species)) |>
  ggplot(aes(x = reorder(species, n), y = n)) +
    geom_col() +
    coord_flip() +
    labs(x = "Species", y = "Count")
```

## External Images

\begin{center}
\includegraphics[width=0.8\textheight]{figures/approx.pdf}
\end{center}

## Math and Footnotes

You can use \LaTeX\ equations:\footnote{The expectation operator $\E$ is a makro, see the file theme/commands.tex for more.}

$$\hat{\beta} = (X^\top X)^{-1}X^\top y, \qquad \E(Y \mid X) = X\beta$$

You can use inline math too, e.g. $\alpha \in \R$.

## Quotes and Blocks

\begin{quote}
"Without data, you’re just another person with an opinion." -- W. Edwards Deming
\end{quote}

\begin{block}{Title}
Use for neutral structure.
\end{block}

\begin{exampleblock}{Title}
Use for examples or recommended actions.
\end{exampleblock}

\begin{alertblock}{Title}
Use for caveats.
\end{alertblock}


# Appendix
\hypertarget{appendix}{}

The start of the backup slides. You can provide an overview here:

\vfill

\begin{tabular}{p{2cm}p{2cm}}
  \overviewbutton{backup_column_details}{Column details}
\end{tabular}

## More details on columns
\hypertarget{backup_column_details}{}

If you want to use lists within columns, you need to explicitly use the \code{itemize} environment:

\begin{columns}[T,totalwidth=\textwidth]
\column{0.4\textwidth}
\begin{itemize}
  \item this
  \item works
  \item well
\end{itemize}

\hfill

\column{0.4\textwidth}
- this
- does
- not
- work
\end{columns}

\returnbutton{buttons_slide}{Return}
